MSDS 6306: Doing Data Science - Case Study 01 - Beers/Breweries Dataset

### 2020-10-11 MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Rmd file edited

```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
require(graphics)
library(tidyverse)
library(magrittr)
library(GGally)
library(ggthemes)
library(plotly)
library(maps)
library(stringr)
library(stringi)
library(mapproj)

@@

#Beer and Breweries data input from CSV files
```{r Beer Data}
# This reads in the Beers data from select folder file Beers.csv.
Beerdata <- read.csv(choose.files(),header = T,sep = ",",na.strings = "NA",fill = TRUE);
head(Beerdata)
nrow(Beerdata)
```

@@

#Summary count of number of ABV values by categorized Ounces of beer
s <- Beerdata1 %>% group_by(Ounces) %>% summarize(ABV,count=n())

>>>>

```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
require(graphics)
library(tidyverse)
library(magrittr)
library(GGally)
library(ggthemes)
library(plotly)
library(maps)
library(stringr)
library(stringi)
library(mapproj)
library(RCurl)
library(readr)
library(rio)

@@

#Beer and Breweries data input from CSV files
```{r Beer Data}
# This reads in the Beers data from select folder file Beers.csv.
Beerdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Beers.csv",header = T,sep = ",",na.strings = "NA",fill = TRUE);
head(Beerdata)
nrow(Beerdata)
```

@@

#Summary count of number of ABV values by categorized Ounces of beer
s <- Beerdata1 %>% group_by(Ounces)%>% summarize(ABV,count=n())
